AMEN tutorial

### 2020-03-06 code/reiter_stam_2003/amen-tutorial.Rmd
CD RMD checks

```{r load-data, cache=TRUE}
## read data and add variables
data = read_dta('/Users/dorffc/Dropbox/Research/nothingbutnet/netsMatter/replications/Reiter_Stam_2003/input/doublereduce.dta')
head(data)
```

@@

## setup result output directory
resultsPath = '/Users/JuamnTellez/Dropbox/papers/netsMatter/replications/Reiter_Stam_2003/output/'
```

@@

```{r run-amen, eval=FALSE}
## select number of cores to locate
cl=makeCluster(4) ; registerDoParallel(cl) # number of clusters depends 
## on how many cores your computer or cluster has

>>>>

```{r load-data, cache=TRUE}
## read data and add variables
data = read_dta('/Users/dorffc/Dropbox/Research/nothingbutnet/netsMatter/replications/Reiter_Stam_2003/input/doublereduce.dta')
#data = read_dta('/Users/JuamnTellez/Dropbox/papers/netsMatter/replications/Reiter_Stam_2003/input/doublereduce.dta')
```

@@

## setup result output directory
#resultsPath = '/Users/JuamnTellez/Dropbox/papers/netsMatter/replications/Reiter_Stam_2003/output/'
resultsPath = '/Users/dorffc/Dropbox/Research/nothingbutnet/netsMatter/replications/Reiter_Stam_2003/output/'
```

@@

```{r run-amen, eval=FALSE}
## select number of cores to locate
cl=makeCluster(6) ; registerDoParallel(cl) # number of clusters depends 
## on how many cores your computer or cluster has
